\chapter{Basics}
\label{ch:basics}

Before delving into the comparative study of automatic 3D model generation techniques, it is crucial to establish a common ground of understanding for the underlying technologies that power these generative methods. This section aims to provide an introductory overview of key concepts and models in the realm of generative machine learning and 3D data representation. The section starts with Variational Autoencoders (VAEs), which serve as probabilistic frameworks for learning complex data representations. Generative Adversarial Networks (GANs) are then discussed, highlighting their unique training dynamics that include both generator and discriminator components. The section further explores the domain of Diffusion Models, focusing on Denoising Diffusion Probabilistic Models (DDPMs), Stochastic Gradient Methods (SGMs), and Stochastic Differential Equations (SDEs), each with their unique approach to data generation. Additionally, the innovative field of Contrastive Language-Image Pre-training (CLIP) is examined, showcasing its ability to bridge natural language and visual data. This provides promising avenues for text-guided 3D model generation. Lastly, various forms of representation of 3D data are examined, including Meshes, Point-Clouds, and Voxels, constituting the foundational structure of 3D objects in computational environments. Proficiency in these representations is required for comprehending the 3D model generation.

\input{chapters/Basics/VAEs}
\input{chapters/Basics/GANs}
\input{chapters/Basics/diffusionModels}
\input{chapters/Basics/CLIP}
\input{chapters/Basics/3Drepresentation}
