\chapter{Comparative Study}~\label{ch:comparative study}

This chapter deals with a systematic evaluation of the previously investigated methods for creating 3D models. This analysis is crucial for understanding the real-world applicability and effectiveness of each method. The aim is to compare the theoretical principles with the practical results and to provide a comprehensive evaluation of the performance of each model under experimental conditions.

The chapter begins with a description of the experimental framework that was created to test these models. This includes the specific conditions, frameworks and parameters used to ensure that the comparison is fair and the results reliable. A detailed examination of the performance metrics is then presented. These metrics are not limited to accuracy and speed, but also include factors such as resource efficiency and versatility of the model, providing a multi-dimensional view of the capabilities of each method.

Finally, the chapter highlights a thorough analysis of the results obtained from these experiments. This section not only presents the data, but also interprets them in the context of the theoretical background, limitations and potential applications of each model. The insights gained here are crucial for anyone who wants to understand the state of the art in 3D modeling and its practical implications in the real world. Through this comparative approach, the chapter aims to bridge the gap between theory and practice and provide a clear overview of the state of each method and its potential future development.

\input{chapters/comparison/experimentalSetup.tex}
\input{chapters/comparison/performanceMetrics.tex}
\input{chapters/comparison/ResultsAndAnalysis.tex}
