\chapter{Models}\label{ch:models}

This chapter presents an in-depth exploration of various models used in the automatic generation of 3D models. It is pivotal as it bridges the theoretical foundations laid in the previous chapters with practical applications and technologies that are developing the field of 3D modeling. It delves into different categories of model generation, specifically focusing on 3D models generated from text and images. This comprehensive analysis not only highlights the diversity and complexity of current methods but also underscores the rapid advancements and potential future developments in this domain.

In this chapter, the journey begins with an examination of models that convert textual descriptions into 3D models. This section is instrumental in understanding how linguistic inputs are interpreted and transformed into visual forms, a process that combines the realms of language processing and visual rendering. Following this, the focus shifts to models that derive 3D structures from 2D images, a process that challenges and expands the traditional boundaries of computer vision and image processing.

Each section within this chapter critically analyzes their methodologies, strengths and limitations. This approach offers a multi-dimensional view of the current state of 3D model generation, equipping the reader with a comprehensive understanding of both the technological intricacies and the practical significance of these models.

\input{chapters/Models/3dFromText}
\input{chapters/Models/3dFromImage}
\input{chapters/Models/3dFromVideo}