\section{Comparative Analysis}\label{comparativeAnalysis}

Conducting a comparative analysis of 3D models presents a challenging endeavor, as the parameters defining their success vary widely based on the intended application. For instance, low-resolution models suffice for real-time rendering in virtual reality or gaming contexts, whereas the film industry demands high-quality renderings. Similarly, in industrial applications, precision down to the millimeter is crucial, necessitating extremely detailed and accurate meshes. This analysis therefore approaches the assessment of generated models from multiple dimensions:

\begin{enumerate}
    \item \textbf{Prompt/Result Fidelity:} This dimension explores the alignment of each model with the original prompt or image. It questions whether the intended subject of the model is recognizable without prior knowledge of the input, thereby assessing the model's fidelity to the intended design.
    \item \textbf{Geometry:} Here, the focus is on the complexity and intricacy of each model. It evaluates whether the models exhibit detailed, fine structures or lean towards a more generalized, simplistic design. 
    \item \textbf{Texture Realism:} This aspect assesses the authenticity and quality of the textures applied to the models. It delves into questions of realism~-~how lifelike do the textures appear?
\end{enumerate}

Following this subjective analysis, the study proceeds to evaluate technical aspects of each model, focusing on parameters such as rendering time, efficiency, and resource utilization. Each method is also subjected to targeted tests tailored to specific criteria. For instance, in scenarios where symmetry is critical, the models are evaluated for their ability to replicate symmetrical designs. In contexts where smoothness is key, special emphasis is placed on the models' topological features. Technical metrics for this analysis are derived from tensorboard data or outputs generated during the model training process. Detailed assessments and quantitative analyses~-~such as the evaluation of symmetry, topology, and the detection of holes or anomalies in the models~-~are examined using Evaluate3D. This custom-developed tool integrates the trimesh Python library \citep{trimesh} to provide insights into the geometric properties of each 3D model.

\input{chapters/comparison/subjective}
\input{chapters/comparison/technical}
 
    
    
    